Particle Interception as a Function of Reynolds Number and Collector Density

### 2020-12-16 code/r2analysis.Rmd
done done with r2analysis

library(tidyverse)
library(cowplot)

@@

p1 <- r2final %>%
  group_by(start, stop) %>%
  summarise(mean_r2 = mean(r2)) %>%
  ggplot(aes(x = as.factor(as.numeric(start)-1), y = as.factor(as.numeric(stop)-1), fill = mean_r2, label = round(mean_r2,3))) +
  geom_tile() +
  geom_text() +
  scale_fill_gradient2(midpoint = .5, limits = c(0,1)) +
  labs(y = "Timesteps Removed from End of Run", 
       x = "Timesteps Removed from Beginning of Run", 
       fill = expression(paste("Mean ",R^{2})))

p2 <- r2final %>%
  group_by(start, stop) %>%
  summarise(min_r2 = min(r2)) %>%
  ggplot(aes(x = as.factor(as.numeric(start)-1), y = as.factor(as.numeric(stop)-1), fill = min_r2, label = round(min_r2,3))) +
  geom_tile() +
  geom_text() +
  scale_fill_gradient2(midpoint = .5, limits = c(0,1)) +
  labs(y = "Timesteps Removed from End of Run", 
       x = "Timesteps Removed from Beginning of Run", 
       fill = expression(paste("Min. ",R^{2})))

p3 <- bind_rows(curvval) %>%
  ggplot(aes(x = as.factor(as.numeric(start)-1), y = as.factor(as.numeric(stop)-1), fill = curv, label = signif(curv, digits = 2))) +
  geom_tile() +
  geom_text() +
  scale_fill_gradient2(low = scales::muted("red"), mid = "white", high = scales::muted("red")) +
    labs(y = "Timesteps Removed from End of Run", 
       x = "Timesteps Removed from Beginning of Run", 
       fill = expression(paste(italic(t^{2})," Coefficient")))

final_plot <- plot_grid(p3, p1, p2, labels = c("(a)","(b)","(c)"), scale = .9)

final_plot
```

>>>>

library(tidyverse)
library(cowplot)
library(scales)

@@

p1 <- r2final %>%
  group_by(start, stop) %>%
  summarise(mean_r2 = mean(r2)) %>%
  ggplot(aes(x = as.factor(as.numeric(start)-1), y = as.factor(as.numeric(stop)-1), fill = mean_r2, label = format(round(mean_r2,2),nsmall = 2))) +
  geom_tile() +
  geom_text() +
  scale_fill_gradient2(midpoint = .5, limits = c(0,1)) +
  labs(y = expression(italic(m)), 
       x = expression(italic(n)), 
       fill = expression(paste("Mean ",R^{2}))) +
  theme(legend.justification = c(0,1))

p2 <- r2final %>%
  group_by(start, stop) %>%
  summarise(min_r2 = min(r2)) %>%
  ggplot(aes(x = as.factor(as.numeric(start)-1), y = as.factor(as.numeric(stop)-1), fill = min_r2, label = format(round(min_r2,2),nsmall=2))) +
  geom_tile() +
  geom_text() +
  scale_fill_gradient2(midpoint = .5, limits = c(0,1)) +
  labs(y = expression(italic(m)), 
       x = expression(italic(n)), 
       fill = expression(paste("Min. ",R^{2}))) +
  theme(legend.justification = c(0,1))

curvtable <- bind_rows(curvval)

p3 <-  curvtable %>%
  ggplot(aes(x = as.factor(as.numeric(start)-1), y = as.factor(as.numeric(stop)-1), fill = curv*10^8, label = format(round(curv*10^8, digits = 1),nsmall = 1))) +
  geom_tile() +
  geom_text() +
  scale_fill_gradientn(colours = c(muted("red"), 
                                   "white", 
                                   muted("blue"), 
                                   "white",
                                   muted("red")),
                       values = rescale(c(min(curvtable$curv),NA,0,NA,max(curvtable$curv)),to = c(0,1))) +
  labs(y = expression(italic(m)), 
       x = expression(italic(n)), 
       fill = expression(paste(italic(t^{2})," Coeff. (",x10^{-8},")"))) +
  theme(legend.justification = c(0,1))

final_plot <- plot_grid(p3, p1, p2, labels = c("(a)","(b)","(c)"), scale = .9, align = "v", ncol = 1)

final_plot

ggsave("../pics/r2analysis.png", final_plot, dpi = 600, height = 7)
